Automated Example Oriented REST API Documenation

### 2017-08-01 introduction.tex
revised tool paper intro

In Chapter~\ref{chapter:demo_paper}, I present a prototype implementation of the aformentioned technique to demonstrate a reusable tool and compare it against the existing REST API documentation tools that rely on custom API description languages. I also present an example where automated test code can be used to generate and maintain REST API documentation using the developed tool.

>>>>

In Chapter~\ref{chapter:demo_paper}, I present a prototype implementation of the aformentioned technique to demonstrate a reusable tool and compare it against the existing REST API documentation tools that rely on custom API description languages. In this prototype implementation, I discuss the process that transforms a number of example HTTP requests and responses into a usable REST API documentation. I also present an example where automated test code is used to generate and maintain a continuously updated REST API documentation using the developed tool.

### 2017-08-01 root.tex
adds the new intro with a greater detail
revised tool paper intro

I am thankful to my supervisor Dr. Frank Maurer for giving me the opportunity and valuable guidance to pursue this research.

I am also thankful to Dr. Craig Anslow for his continuous encouragement and the countless number of hours that he spent to provide feedback about my work.
\newpage
\phantomsection
\altchapter{\bf{Dedication}}
\begin{center}
  To Shahana
\end{center}
\newpage
\phantomsection
\tableofcontents
\pagestyle{plain}
\newpage
\phantomsection
\listoftables
\pagestyle{plain}
\newpage
\phantomsection
\listoffigures
\pagestyle{plain}
\clearpage
\clearpage          % otherwise tables will be numbered wrong
\end{singlespace}
\newpage
\phantomsection
\chapter*{\bf{List of Symbols, Abbreviations and Nomenclature}\hfill} \addcontentsline{toc}{chapter}{List of Symbols}
\listofsymbols
\pagestyle{plain}
\clearpage

@@

In my second study, I investigated the existing literature on API usablity to derive a set of re- quirements that are applicable to REST API documentation and proposed an idea of automatically generating and maintaining REST API documentation from executable code. I found that existing techniques for REST API documentation systems relied on custom API description languagees that are manually maintained as a parallel artifact to the API code, causing potential drift between the actual API and it’s documentation as it evolves over time. By using interception, I have demon- strated that it is possible to automatically record and synthesize the recorded API traffic to generate pragmatic REST API documentation from its test code. Additionally, the technique allows API de- velopers to collaboratively document the API with realistic and executable examples for multiple versions as the API evolves.

>>>>

I am thankful to my supervisor Dr. Frank Maurer for giving me the opportunity and valuable guidance to pursue this research. I am also thankful to Dr. Craig Anslow for his continuous encouragement and the countless number of hours that he spent to provide feedback about my work.

I am grateful to Cisco for allowing me to pursue this research alongside my job. I am grateful to the study participants in my case studies for sharing their time with me on the experiments.
\newpage
\phantomsection
\altchapter{\bf{Dedication}}
\begin{center}
  To my dear wife.
\end{center}
\newpage
\phantomsection
\tableofcontents
\pagestyle{plain}
\newpage
\phantomsection
\listoftables
\pagestyle{plain}
\newpage
\phantomsection
\listoffigures
\pagestyle{plain}
\clearpage
\clearpage          % otherwise tables will be numbered wrong
\end{singlespace}
\newpage
\phantomsection
\chapter*{\bf{List of Symbols, Abbreviations and Nomenclature}\hfill} \addcontentsline{toc}{chapter}{List of Symbols}
\listofsymbols
\pagestyle{plain}
\clearpage

@@

In my second study, I investigated the existing literature on API usablity to derive a set of re- quirements that are applicable to REST API documentation and proposed an idea of automatically generating and maintaining REST API documentation from executable code. I found that existing techniques for REST API documentation systems relied on custom API description languagees that are manually maintained as a parallel artifact to the API code, causing potential drift between the actual API and its documentation as it evolves over time. By using interception, I have demon- strated that it is possible to automatically record and synthesize the recorded API traffic to generate pragmatic REST API documentation from its test code. Additionally, the technique allows API de- velopers to collaboratively document the API with realistic and executable examples for multiple versions as the API evolves.
